TBD

### 2021-03-13 outputs/paper/paper.Rmd
Add line plot

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
library(olsrr)

@@

@@

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = "#e3e2e1",
                colour_x = "#FFA500", 
                colour_xend = "#FF0000",
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
                # TODO: Fix legend 
  labs(x = NULL, y = NULL, title = "Share of wallets reported by country") +
  theme_minimal() +
  scale_color_manual(name = "", values = c("red", "blue") ) +
  theme(panel.grid.major.x = element_line(size = 0.02))

>>>>

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
# install.packages("olsrr")
library(olsrr)

@@

```{r, echo = FALSE, message = FALSE}
#### Define color HEX Code ####
colorRed <- "#E43B2D"
colorOrange <- "#F27E33"
colorBrown <- "#A65629"
colorGray <- "#E3E2E1"
```

@@

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = colorGray,
                colour_x = colorOrange, 
                colour_xend = colorRed,
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
                # TODO: Fix legend 
  labs(x = NULL, y = NULL, title = "Share of wallets reported by country") +
  theme_minimal() +
  scale_color_manual(name = "", values = c("red", "blue")) +
  theme(panel.grid.major.x = element_line(size = 0.02))

```{r, echo = FALSE, message = FALSE}
#### Line chart: Reporting rates as a function of monetary stakes ####

### Report rate: Poland, UK, and USA
dfRateNoMoney <-
  dfMergedNoMoney %>%
  filter(country == "Poland" | country == "UK" | country == "USA")

dfRateMoney <-
  dfMergedMoney %>%
  filter(country == "Poland" | country == "UK" | country == "USA")

### All wallets with big money
dfBigMoney <- 
  dfCleanBehav %>%
  filter(cond == 2) %>%
  group_by(country_2) %>%
  tally()

### Returned wallets with big money
dfReturnedBigMoney <-
  dfCleanBehav %>%
  filter(cond == 2 & response == 100) %>%
  group_by(country_2) %>%
  tally()

### Merge all wallets and returned wallets with money
dfMergedBigMoney <-
  merge(x = dfBigMoney, y = dfReturnedBigMoney, by = "country_2", all.x = TRUE) %>%
  mutate(rating = round(n.y / n.x * 100, 2)) %>%
  rename(country = "country_2") %>%
  rename(total = "n.x") %>%
  rename(returned = "n.y")

### Bind all conditions
dfRateNoMoney["condition"] <- "NoMoney"
dfRateMoney["condition"] <- "Money"
dfMergedBigMoney["condition"] <- "BigMoney"
dfRate3Cond <- rbind(dfRateNoMoney, dfRateMoney, dfMergedBigMoney)

### Sort by condition
dfRate3Cond$condition <- factor(dfRate3Cond$condition, 
                                levels = c("NoMoney", "Money", "BigMoney"))

### Display data in a line graph
ggplot(data = dfRate3Cond,
       aes(x = condition,
           y = rating,
           group = country,
           color = country)) +
    geom_line(size = 1) +
    scale_color_manual(values = c(colorBrown, colorRed, colorOrange)) +
    geom_point(size = 3) +
    theme_bw() +
    theme(axis.line = element_line(colour = "black"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank())
